Portfolio conservation of metapopulations\\under climate change

### 2013-08-07 inst/ms/salmonfolios.tex
Add to ms; move ms to all Pandoc

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{fontspec}
\textheight 20.5cm
\usepackage{setspace}
\usepackage{booktabs}
\setlength{\parskip}{3pt} % changes vertical space between paragraphs
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}

@@

\title{Portfolio conservation of metapopulations under climate change}

\author{
  Sean C. Anderson$^{1*}$, 
  Jonathan W. Moore$^1$,
  Trevor A. Branch?,\\
  Nicholas K. Dulvy$^1$,
  Michelle M. McClure?,
  Andrew B. Cooper$^2$
}
\date{}

@@

\begin{document}
%\onehalfspacing
\linenumbers
\modulolinenumbers[2]
\begin{spacing}{1.3}
%\doublespacing
\maketitle

\noindent
  \textsuperscript{1}Department of Biological Sciences, Simon Fraser
  University, Burnaby BC, V5A 1S6, Canada

\noindent
	\textsuperscript{2}School of Resource and Environmental Management, Simon
  Fraser University, Burnaby, BC, V5A 1S6, Canada

\noindent
Statement of authorship: 
%Contributions by authors should be listed on the title page and will be printed at the end of the manuscript. This statement should be appropriate to the study described in the manuscript and should clarify who designed the study, who performed the research, who provided new methods or materials, and who wrote the manuscript. We encourage concise statements such as “JW performed phylogenetic analyses, MH collected data, performed modeling work and analyzed output data, and PK performed the meta-analysis. MH wrote the first draft of the manuscript, and all authors contributed substantially to revisions.”

\noindent
Running title: 
%(abbreviated form of title) of less than 45 characters including spaces

\noindent
Keywords:
%up to 10

\noindent
Type of article: Letters

\noindent
Abstract:

\noindent
Main text:
%(excluding abstract, acknowledgements, references, table and figure legends), and the number of words in each text box

\noindent
References:

\noindent
Number of figures:

\noindent
Number of tables:

 %- the name and complete mailing address (including telephone and fax numbers and e-mail address) of the person to whom correspondence should be sent
\noindent
	\textsuperscript{*}Corresponding author: Sean C. Anderson; Department of Biological Sciences, Simon Fraser University, Burnaby BC, V5A 1S6; Phone: 1-778-782-3989; E-mail: sean\_anderson@sfu.ca

\clearpage

\include{ms}

>>>>

\documentclass[12pt]{article}
%\documentclass{aastex}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{lineno}
\textheight 20.5cm
\usepackage{setspace}
\usepackage{booktabs}
\usepackage[sectionbib]{chapterbib}
\setlength{\parskip}{9pt} % changes vertical space between paragraphs
\setlength{\parindent}{0cm} 
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}

\makeatletter
\renewcommand\@seccntformat[1]{}
\makeatother

@@

%\title{Portfolio conservation of metapopulations\\under climate change}

%\author{
  %Sean C. Anderson$^{1*}$, 
  %Jonathan W. Moore$^1$,
  %Trevor A. Branch?,\\
  %Nicholas K. Dulvy$^1$,
  %Michelle M. McClure?,
  %Andrew B. Cooper$^2$\\(Order to be discussed)
%}
%\date{}

@@

\begin{document}
%\begin{spacing}{1.1}
%\doublespacing
%\maketitle

%\noindent
  %\textsuperscript{1}Department of Biological Sciences, Simon Fraser
  %University, Burnaby BC, V5A 1S6, Canada

%\noindent
	%\textsuperscript{2}School of Resource and Environmental Management, Simon
  %Fraser University, Burnaby, BC, V5A 1S6, Canada

%\noindent
%\textit{Statement of authorship}: SCA, JWM, NKD, and ABC designed the analyses. SCA wrote the simulation and analyzed the results. SCA and XX \ldots wrote the manuscript. All authors participated in conception, discussion of the results, and manuscript preparation.
%Contributions by authors should be listed on the title page and will be printed at the end of the manuscript. This statement should be appropriate to the study described in the manuscript and should clarify who designed the study, who performed the research, who provided new methods or materials, and who wrote the manuscript. We encourage concise statements such as “JW performed phylogenetic analyses, MH collected data, performed modeling work and analyzed output data, and PK performed the meta-analysis. MH wrote the first draft of the manuscript, and all authors contributed substantially to revisions.”

%\noindent
%\textit{Running title}:
%Portfolio conservation of metapopulations
%(abbreviated form of title) of less than 45 characters including spaces

%\noindent
%\textit{Keywords}: 
%biocomplexity, 
%Modern Portfolio Theory, 
%portfolio effect, 
%prioritization, 
%resource management, 
%range contraction, 
%response diversity, 
%risk assessment, 
%salmon, 
%stochastic simulation 
%(maximum 10)
%%up to 10

%\noindent
%\textit{Type of article}: Letters

%\noindent
%\textit{Words in abstract}: (maximum 150)

%\noindent
%\textit{Words in main text}: (maximum 5000)
%%(excluding abstract, acknowledgements, references, table and figure legends), and the number of words in each text box

%\noindent
%\textit{Number of references}:

%\noindent
%\textit{Number of figures}: 5

%\noindent
%\textit{Number of tables}: 1?

 %- the name and complete mailing address (including telephone and fax numbers and e-mail address) of the person to whom correspondence should be sent
%\noindent
	%\textsuperscript{*}Corresponding author: Sean C. Anderson; Department of Biological Sciences, Simon Fraser University, Burnaby BC, V5A 1S6; Phone: 1-778-782-3989; E-mail: sean\_anderson@sfu.ca

%\end{spacing}
%\clearpage

%\linenumbers
%\modulolinenumbers[2]
\begin{spacing}{1.4}
%\onehalfspacing
\include{ms}
